Viscous Transport in Eroding Porous Media

### 2019-06-03 docs/transport/erosion_transport.tex
do the result section in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have shown that the velocity, shear stress, vorticity, and pressure
of the double-layer potential can all be written in terms of Cauchy
integrals and its first two derivatives.  Therefore, we require
quadrature methods to evaluate the expressions in
equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
periodic, the Trapezoid rule has spectral accuracy.  However, the
integrand is nearly singular if $x$ is close to $\bd\Omega$, and the
quadrature error is arbitrarily large for a fixed resolution.  There
have been a variety of near-singular integration schemes developed, and
we extend a method first outlined by Barnett et
al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
rule}.  This method first uses the density function $\tau(y)$ to compute
the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use of
the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega.
\end{align}

Here, we briefly describe this quadrature method, and then derive a
necessary extension to simulate erosion.  The Barycentric quadrature
rule starts with a quadrature rule with nodes $y_j \in \bd\Omega$ and
weights $w_j$. We use the trapezoid rule because of its superior
accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, as $x$
approaches $\bd\Omega$, the integrand becomes nearly singular and the
quality of the trapezoid rule deteriorates. To eliminate the
nearly-singular integrand, we use the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
\end{align}
Rearranging for $v(x)$, we have
\begin{align}
  v(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y)}{y-x}\, dy}
    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
\end{align}
Of course, the denominator is simply $1$, but applying a quadrature rule
to both integrands results in a uniform bound on the quadrature error.
Differentiating Cauchy's integral theorem, the derivative of $v$ is
\begin{align}
  v'(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
\end{align}

@@

The flow rate increases exponentially with growth rate close to $\ln10^4$. 
 }

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have shown that the velocity, shear stress, vorticity, and pressure
of the double-layer potential can all be written in terms of Cauchy
integrals and its first two derivatives.  Therefore, we require
quadrature methods to evaluate the expressions in
equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
periodic, the trapezoid rule has spectral accuracy.  However, the
integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
quadrature error is arbitrarily large for a fixed resolution.  There
have been a variety of near-singular integration schemes developed, and
we extend a method first outlined by Barnett et
al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
rule}.  This method first uses the density function $\tau(y)$ to compute
the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use of
the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega.
\end{align}

Here, we briefly describe the Barycentric quadrature method, and then
derive a necessary extension to simulate erosion.  The method starts
with a quadrature rule with nodes $y_j \in \bd\Omega$ and weights $w_j$,
$j=1,\ldots,N$.  We use the trapezoid rule because of its superior
accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, at a
fixed resolution, if $x$ is sufficiently close to $\bd\Omega$, each of
the integrands in equation~\eqref{eqn:cauchy} are nearly-singular and
the quadrature error is prohibitively large.  However, the trapezoid
rule applied to the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
\end{align}
has a uniformly bounded error since the integrand is not nearly-singular
as $x$ approaches $\bd\Omega$.  That is,
\begin{align}
  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0.
\end{align}
Rearranging for $v(x)$, we have
\begin{align*}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j},
\end{align*}
which is simply the trapezoid rule applied to the two integrals in the
identity
\begin{align}
  v(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y)}{y-x}\, dy}
    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
\end{align}
Of course, the denominator is simply $1$, but by applying the trapezoid
rule to both integrands, the result is an error with a uniform bound.
To compute $v'(x)$, the identity
\begin{align}
  v'(x) = \frac{\int\limits_{\bd\Omega} 
    \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
  {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy},
\end{align}
is used, and applying the trapezoid rule
\begin{align}
  v'(x) \approx \frac{\sum\limits_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
\end{align}

@@

The flow rate increases exponentially with growth rate close to $\ln10^4$.

In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect of the geometrical structure on fluid velocity field. }
